---
title: "explore_bank"
author: "R. Krasser"
date: "18 Mai 2020"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

library(tidyverse)
library(explore)
```

## Dataset

Using Bank Marketing Dataset from https://archive.ics.uci.edu/ml/datasets/bank+marketing

This dataset is public available for research. The details are described in [Moro et al., 2014].

[Moro et al., 2014] S. Moro, P. Cortez and P. Rita. A Data-Driven Approach to Predict the Success of Bank Telemarketing. Decision Support Systems, Elsevier, 62:22-31, June 2014

The target-variable is called "y" - has the client subscribed a term deposit? (binary: 'yes','no')

## Read Data

```{r}
data <- readr::read_delim("bank-additional.csv", 
                   ";", escape_double = FALSE, trim_ws = TRUE)

data %>% describe_tbl(target = y)
```

```{r}
data %>% describe()
```

## Data Exploration

```{r fig.height=total_fig_height(data)}
data %>% 
  explore_all()
```

## Data Understanding

```{r}
data %>% explore(age)
```

```{r}
data %>% describe(age)
```

So, there are customer with age between 18 and 88, the median is 35 years. There is a "peak" at age 30-35. No customer with unknown age.

```{r}
data %>% explore(marital)
```

60.9% of customers are married, 28% single.

```{r}
data %>% explore(age, marital)
```

There is a pattern between age and marital. Singles have lowest age.

```{r}
data %>% explore(job)
```

```{r}
data %>% explore(age, job)
```

```{r}
data %>% explore(education)
```

## Data+Target Exploration

```{r fig.height=total_fig_height(data)}
data %>% 
  explore_all(target = y, split = FALSE)
```

## Predit Target

```{r}
data %>% explore(y)
```

In the data are 10.9 cases with y = "yes"

```{r}
data %>% explain_tree(target = y, minsplit = 300, maxdepth = 4)
```

